\TheTitle

### 2017-07-10 paper/study.tex
Linvis design and implementation
Adding method details
Adding accuracy metric details for the summarization tasks. Also more
details for measuring the timing from the videos.

\subsection{Questions and Tasks}
\label{sub:questions}

@@

@@

\begin{figure}[bpt]
  \centering
\begin{tabular}{ m{1.5cm} m{3cm} }
  \includegraphics[height=0.5in]{figures/commits/1-commit.pdf} &
  \includegraphics[height=1in]{figures/commits/7-commits.pdf}\\
\end{tabular}
  \caption{The merge trees used in the user study, 
    containing one and seven commits, respectively.}
  \label{fig:commit_1}
\end{figure}

@@

\dmg{this is still methodology.}

We recorded the audio and screen capture video for each participant in
the study for further analysis.
\dmg{you don't need this sentence, it is redundant}
After capturing the information, we
extracted various metrics from the videos.
\dmg{ you don't record, you measure}
From the conceptual tasks, we
recorded the time in seconds, and the answer for the question. We
extracted three metrics for the summarization tasks, the time in
seconds, the correctness, and the accuracy.
\dmg{and then somethings you are over precise :): correctness is simply whether their answer to the task was correct or not}
Correctness is a binary
value, it is true if the response was correct and false if the response
was incorrect.
\dmg{if you are going to use this metric, you need to define precisely. remember, you are giving this to somebody else
  to implement}
The accuracy is measures in distance from the correct
value. An accuracy of zero indicates a correct answer. All tasks in the
summarization tasks include an accuracy metric except T7, which will
only be right or wrong, and therefore cannot meaningfully be measured by
a distance.

@@

In Figure~\ref{fig:summarization_results}, we see all of the
correctness, accuracy, and timing results. The first row of plots are
the correctness results. We see in all cases except for T10, that the
number of instances of a correct result with \tool is roughly the same
as the number of incorrect instances with Gitk. We test each task with
the McNemar Chi-square test~\cite{McNemar1947}.

@@

With the McNemar's tests, we analyze the participants that change from
being correct with one tool to being incorrect with the other. This does
not take into account the number of people who were able to provide the
correct answer for both tools, nor the people who were incorrect for both
tools. The results show whether providing the participants with \tool
over the current standard, gitk, improves the correctness of the
summarization tasks among the participants. We show the results for the
number of people who were, with both tools, correct, incorrect, and
changed in Table~\ref{tab:correctness_table}.

In all cases, except for task T10, we saw statistically significant
results suggesting that we reject the null hypothesis. We tested each
correctness with an $\alpha = 0.005$. The $\chi^2$ test value with one
degree of freedom is $7.879$.

@@

Among the 12 pariticipants, there was nearly unanimous agreement that
for conceptual understanding and summarization tasks, \tool was easier
to work with than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations. Three participants suggested that someone with a
professional understanding of Gitk and the git commandline may be to
extract the a good conceptual understanding from the DAG, and perform
the summarization tasks from the commandline. One of these three
participants said that they would prefer to have both tools available,
as they are able to complement eachother.

>>>>

\subsection{Tasks}
\label{sub:tasks}

@@

% TODO: Move to methodology
The participants were given the choice of Gitk or the git command line
tools to perform the tasks .

@@

\begin{figure}[bpt]
  \centering
\begin{tabular}{ m{1.5cm} m{3cm} }
  \includegraphics[height=0.5in]{figures/commits/1-commit.pdf} &
  \includegraphics[height=1in]{figures/commits/7-commits.pdf}\\
\end{tabular}
  \caption{The merge trees used in the user study,
    containing one and seven commits, respectively.}
  \label{fig:study_commits}
\end{figure}

@@

\dmg{this is still methodology.}
% TODO: Move to methodology
We recorded the audio and screen capture video for each participant in
the study for further analysis.
\dmg{you don't need this sentence, it is redundant}
After capturing the information, we
extracted various metrics from the videos.
\dmg{ you don't record, you measure}
From the conceptual tasks, we
recorded the time in seconds, and the answer for the question. We
extracted three metrics for the summarization tasks, the time in
seconds, the correctness, and the accuracy.

The correctness metric measures whether the answer was correct or
incorrect.

The accuracy metric measures the distance from the correct
answer. In task T4, the merges are important, and the order of those
merges is important to the answer. For this task, we use the edit
distance, which will increment if adding merges, removing merges, and
changing the order of the merges is necessary. T5 only asks for the set
of commits, so the order is not important, but the distance will
increase if adding or removing commits is necessary for getting the
correct answer. In T6 and T8 the answer is a single number, so the
distance is simply the difference between the answer provided and the
correct answer. In T7, there is only a single answer that is correct, so
the correctness metric and accuracy are the same, for this reason we do
not measure the accuracy of this task. The answer for T9 is similar in
requirements to T5, only asking for the set of files that had the most
changes. We use the same distance function in T9 and T10 as we did in
T5, measuring the number of items that must be added and removed from
the answer in order to change the response into the correct answer. % TODO: reword
T9 appears to be similar to T7 in that there is only a single file name
that must be provided, but in \comA, two files are modified the same
amount and are both the correct answer. In order to provide the correct
answer, the participant must be able to identify both files. In all
means of accuracy measurement, a correct answer will have a distance of
zero, while a non-zero distance indicates an incorrect answer.

The timing metric is measured from the video. We begin timing the task
at the end of the question, and stop timing before the last modification
to the answer. For this reason, it is possible for times to overlap
between tasks if the participant changes their answer after answering
another question. This will also modify the answer used for measuring
the accuracy.

@@

In Figure~\ref{fig:summarization_results}, we see all of the
correctness, accuracy, and timing results. The first row of plots are
the correctness results. \dmg{be more direct: we see that linvis outperforms gitk by a large margin (then you can
  clarify with the statement you have below; otherwise you are asking the reader to make that connection; don't leave
  that to chance. be explicit on what the results tell you, at the high level.)}
 We see in all cases except for T10, that the
number of instances of a correct result with \tool is roughly the same
as the number of incorrect instances with Gitk.
\dmg{you don't test the task. You test what? the statistical significance than one tool is better than the other? Again,
be explicit}
We test each task with
the McNemar Chi-square test~\cite{McNemar1947}.\dmg{don't break the paragraphs here.. you keep talking about the
  test. If you need to break them, break them before this sentence, not after}

@@

\dmg{McNemar is used to test if there was an effect on the tool used in the correctness of the answers of the
  users. It is not an analysis of the participants. Don't elaborate on what it does or does not. Just leave it at what
  it does: if you want to be precise you can say it ``marginal homogeneity'' of the answers}

With the McNemar's tests, we analyze the participants that change from
being correct with one tool to being incorrect with the other. \dmg{Again, never, ever, use a pronom like this to start
  a stence. State that this is instead: The McNemar test..., but i vote for removing this info} This does
not take into account the number of people who were able to provide the
correct answer for both tools, nor the people who were incorrect for both
tools. \dmg{this is better, see my comment before this paragraph, you can use this sentence instead, except: not the
  results: the test is used to test the hypothesis that ...} The results show whether providing the participants with \tool
over the current standard, gitk, improves the correctness of the
summarization tasks among the participants. \dmg{Change it to Table shows..., we don't show, we wrote} We show the results for the
number of people who were, with both tools, correct, incorrect, and
changed in Table~\ref{tab:correctness_table}.

In all cases, except for task T10, \dmg{we don't ``see'', ``these is'' instead: in all cases.. there the differences
  are statistically significant} we saw statistically significant
results \dmg{remove suggesting} suggesting that we reject the null hypothesis \dmg{did you tell us what the null hypo
  is?}. \dmg{say this before making conclusions about the results} We tested each
correctness with an $\alpha = 0.005$. The $\chi^2$ test value with one
degree of freedom is $7.879$.\dmg{what is this number? what is it used for? where does it come from?}

@@

Among the 12 pariticipants, there was nearly unanimous agreement that
for conceptual understanding and summarization tasks, \tool was easier
to work with than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations. Three participants suggested that someone with a
professional understanding of Gitk and the git commandline may be to
extract the a good conceptual understanding from the DAG, and perform
the summarization tasks from the commandline. One of these three
participants said that they would prefer to have both tools available,
as they are able to complement each other.
